### 2015-05-12 whoop.tex
fix

A \emph{concurrent program} is described by a finite set of
\emph{shared} variables, $\sharedvars$, a finite set of mutexes,
$\mutexes$, and a finite set of \emph{thread templates}.  A thread
template, $T$, consists of a finite set of procedures,
$\procedures{T}$, and a finite set of private variables,
$\variables{T}$.  A designated procedure, procedure $\mainforthread{T}
\in \procedures{T}$, denotes the starting point for execution of a
template by a thread.  A procedure in $\procedures{T}$ is
represented by a control flow graph of basic blocks, where each block
contains a sequence of statements.  A basic block either has a single
successor or a pair of successors.  In the latter case, an \emph{exit
  condition} over thread-private variables determines, at runtime, the
successor to which control should flow on block exit.

The forms of statements are shown in Figure~\ref{fig:statements}, and
include designated statements for reading from and writing to shared
variables.  In particular, shared variables may not appear in
arbitrary expressions.  This restriction simplifies our presentation
of lockset instrumentation, below, and a program that does not satisfy
this restriction can be trivially pre-processed into one that does
through the introduction of additional private temporaries to record
values read from the shared state.  We do not specify the form of
expressions, nor the types of variables, assuming a standard set of
data types and operations.

>>>>

A \emph{concurrent program} is described by a finite set of \emph{shared} variables, $\sharedvars$, a finite set of mutexes, $\mutexes$, and a finite set of \emph{thread templates}.  A thread template, $T$, consists of a finite set of procedures, $\procedures{T}$, and a finite set of private variables, $\variables{T}$.  A designated procedure, $\mainforthread{T} \in \procedures{T}$, denotes the starting point for execution of a template by a thread.  A procedure in $\procedures{T}$ is represented by a control flow graph of basic blocks, where each block contains a sequence of statements.  A basic block either has a single successor or a pair of successors.  In the latter case, an \emph{exit condition} over thread-private variables determines, at runtime, the successor to which control should flow on block exit.

The forms of statements are shown in Figure~\ref{fig:statements}, and include designated statements for reading from and writing to shared variables.  In particular, shared variables may not appear in arbitrary expressions.  This restriction simplifies our presentation of lockset instrumentation, below, and a program that does not satisfy this restriction can be trivially pre-processed into one that does via the introduction of additional private temporary variables to record values read from the shared state.  We do not specify the form of expressions, nor the types of variables, assuming a standard set of data types and operations.
